Pillar 2 - Topic Modeling

### 2019-03-01 Pillar 2 - Topic Modeling.Rmd
eval=f

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
```

```{r library, message = FALSE}
library(tidyverse)
library(tidytext)

@@

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data}
load("output/data_pillar_2.RDATA")

# Only keep course descriptions and overviews from most recent year
d_description <- d_description %>%
  filter(
    `Academic Year` == "2018-2019"
  )

d_overview <- d_overview %>%
  filter(
    `Academic Year` == "2018-2019"
  )
```

@@

# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

First we set the control for the test.
```{r controls}
my_control <- list(

@@

  burnin = 100,
  iter   = 5000,
  thin   = 100

@@

From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics. Then we save them in the `Output`folder and in the ``Recommender System` folder.
```{r LDA fit, cache = TRUE}
n_topics <- c(35, 35, 40)
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
                      eval = FALSE)
```

```{r library, message = FALSE, eval = TRUE}
library(tidyverse)
library(tidytext)

@@

# Setup
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_AoD`, `d_assessment`, `d_course`, `d_description`, `d_manual`, `d_overview`, `d_transcript`, and a list `lists`.
For `d_description` and `d_overview`, we keep only the most recent year.
```{r import data, eval = TRUE}
load("output/data_pillar_2.RDATA")

# Only keep course descriptions and overviews from most recent year
d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```

@@

# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdmxxxxx}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

First we set the control for the test.
```{r controls, eval = TRUE}
my_control <- list(

@@

  burnin = 1000,
  iter   = 5000,
  thin   = 100

@@

From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics. Then we save them in the `Output`folder and in the ``Recommender System` folder.

#NEW
# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_cast <- d_text %>% map(my_cast_tdm)

```{r my_LDA, eval= TRUE}

#my_LDA
my_LDA <- function(n_topics, corpus){

  LDA_model <- LDA(
    x       = corpus,
    k       = n_topics,
    method  = "Gibbs",
    control = my_control
    )
}

```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

  n_topic = seq(from = 2, to = 80, by = 2)

  ) %>%

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```

```{r saving models, eval= TRUE}
save(topic_model,
     file = "Output/topic_model.RDATA")

save(topic_model,
     file = "App/Recommender System/topic_model.RDATA")
```

```{r LDA fitxxxxxxx, cache = TRUE}
n_topics <- c(35, 35, 40)
levels   <- c("description", "overview", "manual")
list_nam <- character(0)
